Plots and Data Summaries

### 2024-12-15 analysis.qmd
Rearrange districts

```{r}
#| label: tbl-summary
#| tbl-cap: Summary of housing data.
hsp |>
  mutate(
    price = price / 1000,
    storeys = factor(
      ifelse(storeys >= 3, "3+", as.character(storeys)),
      levels = c("1", "2", "3+")
    )
  ) |>
  tbl_summary(
    include = c(price:baths),
    by = district,
    missing = "no", 
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous2() ~ c("{mean} ({sd})", Range = "{min} - {max}", "{median} ({p25}, {p75})")
    ),
    label = list(
      price = "Price (BND 1,000)",
      type = "Property type",
      plot_area = "Plot area (acres)",
      floor_area = "Floor area (sq. ft.)",
      storeys = "Number of storeys",
      status = "Development status",
      tenure = "Land tenure",    
      beds = "Number of bedrooms",
      baths = "Number of bathrooms"
    ),
    digits = list(
      baths = 1,
      beds = 1
    )
  ) |>
  add_overall() |>
  add_n() |>
  modify_header(label ~ "**Variable**")
```

>>>>

```{r}
#| label: tbl-summary
#| tbl-cap: Summary of housing data.
hsp |>
  mutate(
    price = price / 1000,
    storeys = factor(
      ifelse(storeys >= 3, "3+", as.character(storeys)),
      levels = c("1", "2", "3+")
    ),
    district = gsub("Brunei Muara", "Brunei-Muara", district),
    district = factor(district, levels = c("Brunei-Muara", "Belait", "Tutong", "Temburong"))
  ) |>
  tbl_summary(
    include = c(price:baths),
    by = district,
    missing = "no", 
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous2() ~ c("{mean} ({sd})", Range = "{min} - {max}", "{median} ({p25}, {p75})")
    ),
    label = list(
      price = "Price (BND 1,000)",
      type = "Property type",
      plot_area = "Plot area (acres)",
      floor_area = "Floor area (sq. ft.)",
      storeys = "Number of storeys",
      status = "Development status",
      tenure = "Land tenure",    
      beds = "Number of bedrooms",
      baths = "Number of bathrooms"
    ),
    digits = list(
      baths = 1,
      beds = 1
    )
  ) |>
  add_overall() |>
  add_n() |>
  modify_header(label ~ "**Variable**")
```
